{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-06 Paper/main.tex
Reference added
Rendering

	One very important question in this context is how the coefficients $a_j \quad j \in \mathcal{I}$ are derived given a function $x(t)$. For the purposes of this paper, this process will remain a blackbox, but detailed information on the derivation of these coefficients can be found in {\color{red} ADD CITATION!!!} \\
	Three examples of bases often used to approximate elements of $\mathbb{L}^2[0,1]$ in practice and in the later parts of this paper are explained in the following.

@@

	Adress problem of monomials again --> (This could be solved using orthogonal polynomials like Legendre polynomials, see \citep{Dattoli_2001})

@@

	\subsection{Basis Plots}

>>>>

	One very important question in this context is how the coefficients $a_j \quad j \in \mathcal{I}$ are derived given a function $x(t)$. For the purposes of this paper, this process will remain a blackbox, but detailed information on the derivation of these coefficients can be found in {\color{red} ADD CITATION!!!} \\
	Three examples of bases often used to approximate elements of $\mathbb{L}^2[0,1]$ in practice and in the later parts of this paper are explained in the following. Diagrams showing a number of basis functions from these bases are shown in Part \ref{Basis_Plots} of the Appendix.

@@

	Adress problem of monomials again --> (This could be solved using orthogonal polynomials like Legendre polynomials, see \cite{Dattoli_2001})

@@

	\subsection{Basis Plots}\label{Basis_Plots}
